PDBF Testdokument

### 2015-03-03 test.tex
!

\DBSQLText{CREATE TABLE table1 (column1 INTEGER, column2 DATE, column3 FLOAT);}
\DBSQLFile{somedb.sql}
\DBSQLJDBC{jdbc:postgresql://localhost:5432/postgres}{postgres}{test}{testtest, dim_time} %dim_compiler, dim_dataset, dim_implementation, dim_layout, dim_query, dim_machine, fact_experiment

>>>>

\DBSQLText{CREATE TABLE table1 (column1 INTEGER, column2 DATE, column3 FLOAT);}
\DBSQLFile{somedb.sql}
\DBSQLJDBC{jdbc:postgresql://localhost:5432/postgres}{postgres}{test}{testtest, dim_time, dim_compiler, dim_dataset, dim_implementation, dim_layout, dim_query, dim_machine, fact_experiment}%
